\begin{rSection}{Projects}
\vspace{0.12cm}
{\bf The Forge}
\hspace{2 cm}{Python, AI, GitHub}
\hfill{\href{https://github.com/a-curious-coder/theforge}{https://github.com/a-curious-coder/theforge}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Developed an intelligent CV generator to create tailored resumes for users.
    \item[$\bullet$] Leveraged AI to analyze job descriptions and generate customizable templates.
    \item[$\bullet$] Employed GitHub for version control and collaborative development processes.
    \item[$\bullet$] Integrated user feedback to enhance the resume-building experience effectively.
    \item[$\bullet$] Created and documented API endpoints to ensure seamless data interaction across platforms.
\end{itemize}
\vspace{0.12cm}
{\bf MVC Grid Demo}
\hspace{2 cm}{ASP.NET Core, MVC, GitHub}
\hfill{\href{https://mvcgriddemo.callummclennan.dev/}{https://mvcgriddemo.callummclennan.dev/}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Built an ASP.NET Core MVC application demonstrating advanced grid functionalities.
    \item[$\bullet$] Utilized the MVCGrid library for effective dynamic data presentation and management tasks.
    \item[$\bullet$] Implemented DevOps practices to optimize and streamline deployment processes effectively.
    \item[$\bullet$] Created a responsive design for enhanced user accessibility and experience.
    \item[$\bullet$] Implemented performance metrics to continuously improve application efficiency.
\end{itemize}
\vspace{0.12cm}
{\bf Neurosight}
\hspace{2 cm}{Deep Learning, Python, Flask}
\hfill{\href{https://neurosight.callummclennan.dev}{https://neurosight.callummclennan.dev}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Developed a deep learning model to classify Alzheimer's disease with high accuracy.
    \item[$\bullet$] Analyzed medical and MRI scan data to generate valuable insights and predictive outcomes.
    \item[$\bullet$] Employed Flask for back-end development, enabling the creation of robust and efficient APIs.
    \item[$\bullet$] Employed Docker for containerization, ensuring consistent deployment environments.
    \item[$\bullet$] Collaborated with a cross-functional team to iterate on model improvements.
\end{itemize}
\vspace{0.12cm}
{\bf INeedAQRCode}
\hspace{2 cm}{Flask, Python, JavaScript}
\hfill{\href{https://ineedaqrcode.com}{https://ineedaqrcode.com}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Created a user-friendly website for generating QR codes using Flask framework.
    \item[$\bullet$] Integrated JavaScript for dynamic content rendering and improved UX design.
    \item[$\bullet$] Implemented RESTful APIs for efficient service interactions and data handling.
    \item[$\bullet$] Used GitHub Actions for automated testing and deployment processes effectively.
    \item[$\bullet$] Emphasized UI/UX design to improve user engagement and enhance overall site usability.
\end{itemize}
\vspace{0.12cm}
{\bf Evolario}
\hspace{2 cm}{Python, AI, GitHub}
\hfill{\href{https://github.com/a-curious-coder/evolario}{https://github.com/a-curious-coder/evolario}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Developed a simplified clone of AGAR.IO for testing AI agents using Python.
    \item[$\bullet$] Implemented game mechanics focusing on adaptability and performance metrics.
    \item[$\bullet$] Used GitHub for collaborative version control within a remote development team.
    \item[$\bullet$] Developed comprehensive documentation to streamline onboarding and ensure project maintenance.
    \item[$\bullet$] Enhanced framework using AI algorithms to improve scalability and performance of agents.
\end{itemize}
\vspace{0.12cm}
{\bf Rubik's Cube Solver}
\hspace{2 cm}{Processing, AI, GitHub}
\hfill{\href{https://github.com/a-curious-coder/rubiks-cube-solver}{https://github.com/a-curious-coder/rubiks-cube-solver}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Created an algorithmic solver for Rubik's Cube using the Processing language.
    \item[$\bullet$] Created user interface for real-time solutions, enhancing interactive user experiences.
    \item[$\bullet$] Analyzed algorithm performance for optimal solution timings and steps used.
    \item[$\bullet$] Implemented AI techniques to improve the efficiency of the solving algorithm significantly.
    \item[$\bullet$] Published a project on GitHub, enhancing open-source communities through collaboration.
\end{itemize}
\vspace{0.12cm}
{\bf AAWTattoo}
\hspace{2 cm}{Django, Python}
\hfill{\href{https://aawtattoo.com}{https://aawtattoo.com}}
\begin{itemize}[label=\myfancylabel, leftmargin=0.5cm, topsep=-5pt, itemsep=-1ex]
\setlength\itemsep{-0.25cm}
    \item[$\bullet$] Developed a Django-based booking site for tattoo artists to manage appointments.
    \item[$\bullet$] Focused on user-friendly navigation and seamless user interface experiences.
    \item[$\bullet$] Developed SQL database models to enhance data management efficiency and organization.
    \item[$\bullet$] Employed REST APIs for integrating external services and enhancing functionality.
    \item[$\bullet$] Launched the site with an emphasis on user feedback for iterative improvements.
\end{itemize}
\end{rSection}